An indexed construction of semi-cubical types

### 2021-07-01 paper/paper.tex
[paper] Cleanup in progress

\documentclass[a4paper]{article}

\usepackage{hyperref, fullpage, amssymb, stmaryrd, url, color, amsmath}
\usepackage{bookmark, fontspec}
\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false,doi=false]{biblatex}

@@

\include{macros}
\newcommand{\Type}{\mathsf{Type}}
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Prop}{\mathsf{Prop}}
\newcommand{\refl}[1]{\mathsf{refl}\,{#1}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\mathsf{refl^{\mathrm{dep}}}\,{#1}}
\newcommand{\mluniv}{\mathsf{U}}
\newcommand{\Jdep}[2]{\mathsf{J}\;{#1}\;{#2}}

@@

\newcommand{\sort}[1]{\mathsf{U}_{#1}}
\newcommand{\univ}{\boxempty}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

@@

\newcommand{\defeq}{\triangleq}
\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

@@

\newcommand{\homoname}{}
\newcommand{\heteroname}{het}
\newcommand{\mycubsetcomp}[2]{\mathsf{cubset}_{#1}^{=#2}}

@@

\newcommand{\mybox}[1]{\mathsf{{\homoname}box}_{#1}}
\newcommand{\mylayer}[1]{\mathsf{{\homoname}layer}_{#1}}
\newcommand{\mycube}[1]{\mathsf{{\homoname}\cubeovername}_{#1}}
\newcommand{\downbox}[2]{\mathsf{sub{\homoname}box}_{#1}^{#2}}
\newcommand{\downlayer}[2]{\mathsf{sub{\homoname}layer}_{#1}^{#2}}
\newcommand{\downcube}[2]{\mathsf{sub{\homoname}cube}_{#1}^{#2}}
\newcommand{\cohbox}[2]{\mathsf{coh{\homoname}box}_{{#1}}^{{#2}}}
\newcommand{\cohlayer}[2]{\mathsf{coh{\homoname}layer}_{#1}^{#2}}
\newcommand{\cohcube}[2]{\mathsf{coh{\homoname}\cubeovername}_{#1,#2}}
\newcommand{\myfullbox}[1]{\mathsf{full{\homoname}box}_{#1}}
\newcommand{\fulldownbox}[2]{\mathsf{subfull{\homoname}box}_{#1}^{#2}}
\newcommand{\fulldowncube}[2]{\mathsf{subfull{\homoname}cube}_{#1}^{#2}}

@@

\newcommand{\expandheterocube}[2]{\mathsf{expand\Cubeovername}_{#1}^{#2}}
\newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
\newcommand{\expanddownbox}[2]{\mathsf{expandsub{\homoname}box}_{#1}^{#2}}
\newcommand{\expanddownlayer}[2]{\mathsf{expandsub{\homoname}layer}_{#1}^{#2}}
\newcommand{\expanddowncube}[2]{\mathsf{expandsub{\homoname}cube}_{#1}^{#2}}

\newcommand{\depdownbox}[2]{\mathsf{depsub{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayer}[2]{\mathsf{depsub{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncube}[2]{\mathsf{depsub{\homoname}cube}_{#1}^{#2}}
\newcommand{\depdownboxbis}[2]{\mathsf{depsublift{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayerbis}[2]{\mathsf{depsublift{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncubebis}[2]{\mathsf{depsublift{\homoname}cube}_{#1}^{#2}}
\newcommand{\depdownboxter}[2]{\mathsf{depsublift{\homoname}box'}_{#1}^{#2}}
\newcommand{\depdownlayerter}[2]{\mathsf{depsublift{\homoname}layer'}_{#1}^{#2}}
\newcommand{\depdowncubeter}[2]{\mathsf{depsublift{\homoname}cube'}_{#1}^{#2}}

\newcommand{\depcohbox}[2]{\mathsf{depcoh{\homoname}box}_{#1}^{#2}}
\newcommand{\depcohlayer}[2]{\mathsf{depcoh{\homoname}layer}_{#1}^{#2}}
\newcommand{\depcohcube}[2]{\mathsf{depcoh{\homoname}cube}_{#1}^{#2}}
\newcommand{\depcohboxbis}[2]{\mathsf{depcohlift{\homoname}box}_{#1}^{#2}}
\newcommand{\depcohlayerbis}[2]{\mathsf{depcohlift{\homoname}layer}_{#1}^{#2}}
\newcommand{\depcohcubebis}[2]{\mathsf{depcohlift{\homoname}cube}_{#1}^{#2}}
\newcommand{\depcohboxter}[2]{\mathsf{depcohlift{\homoname}box'}_{#1}^{#2}}
\newcommand{\depcohlayerter}[2]{\mathsf{depcohlift{\homoname}layer'}_{#1}^{#2}}
\newcommand{\depcohcubeter}[2]{\mathsf{depcohlift{\homoname}cube'}_{#1}^{#2}}

@@

\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\depdownboxtype}[2]{\mathsf{Subdep{\homoname}box}_{#1}^{#2}}
\newcommand{\depdownlayertype}[2]{\mathsf{Subdep{\homoname}layer}_{#1}^{#2}}
\newcommand{\depdowncubetype}[2]{\mathsf{Subdep{\homoname}\cubeovername}_{#1}^{#2}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
\newcommand{\downcubetype}[2]{\mathsf{Sub\cubeovername}_{#1}^{#2}}
\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Coh\cubeovername}_{#1}^{#2}}
\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myfullcube}[1]{\mathsf{full{\homoname}cube}_{#1}}
\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\unittype}{\mathsf{unit}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}

\newcommand{\mycubset}[1]{\mathsf{cubset}_{#1}}
\newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
\newcommand{\partialcubset}[2]{\mathsf{cubset}_{#1}^{<#2}}
\newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
\newcommand{\mydepcubsetfrom}[2]{\mathsf{dephomocubset}_{#1}^{\geq#2}}
\newcommand{\mydepcubsetcomp}[2]{\mathsf{dephomocubset}_{#1}^{=#2}}
\newcommand{\deppartialcubset}[2]{\mathsf{dephomocubset}_{#1}^{<#2}}
\newcommand{\properheterocubetype}[2]{\mathsf{Filler}_{#1}^{#2}}

@@

\newcommand{\typecubset}{\mathsf{typecubset}}
\newcommand{\mysymcubset}{\mathsf{symcubset}}
\newcommand{\issymcubset}{\mathsf{issymcubset}}
\newcommand{\partialsymcubset}{\mathsf{symcubset}}
\newcommand{\mypermute}{\mathsf{permute}}
\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
\newcommand{\hascomp}{\mathsf{hascomp}}
\newcommand{\tube}[1]{\mathsf{{\homoname}tube}_{#1}}
\newcommand{\propercube}[1]{\mathsf{proper{\homoname}filler}_{#1}}
\newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
\newcommand{\border}[1]{\mathsf{{\homoname}border}_{#1}}
\newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
\newcommand{\cohbordertype}[1]{\mathsf{Cohboxofcube}_{#1}}
\newcommand{\myheteroborder}[1]{\mathsf{{\heteroname}border}_{#1}}
\newcommand{\fullheterocubetype}[2]{\mathsf{fullCube}_{#1}^{#2}}
\newcommand{\fullheterocube}[1]{\mathsf{full{\heteroname}cube}_{#1}}
\newcommand{\heterotubetype}[1]{\mathsf{Tube}_{#1}}
\newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
\newcommand{\mygroundedcube}[1]{\mathsf{grounded{\homoname}cube}_{#1}}
\newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
\newcommand{\mygroundedheterocube}[1]{\mathsf{grounded{\heteroname}cube}_{#1}}
\newcommand{\reflexive}[1]{\mathsf{reflexive}_{#1}}
\newcommand{\permutation}{\mathsf{permutation}}
\newcommand{\diagonal}{\mathsf{diagonal}}
\newcommand{\connection}{\mathsf{connection}}
\newcommand{\diagprop}{\mathsf{diag}}
\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}

@@

\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
\newcommand{\Simplex}[1][n]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
\newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}

@@

\section{The intuition from \SSet}

\section{Semi-cubical sets}
\label{sec:truncated-cubical-sets}

@@

          \myfullcube{l}^{n}     & (D,E)                                                                                          & \defeq & \Sigma d:\myfullbox{l}^{n}(D).\, E.\mathsf{rel}(d) \\

@@

          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}^{n}(\hd(D)))                                       & :      & \sort{l}                                           \\

@@

          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                       & :      & \myfullbox{l}^{n}(\hd(D))                          \\

>>>>

\documentclass{article}

\usepackage[allbordercolors={.192157 .76862 .28627}]{hyperref} % Emerald Green
\usepackage{bookmark, titling, fontspec, xargs, multirow, polyglossia, luacode, fancyhdr, lastpage, amssymb}
\usepackage{listings, color, soulutf8, graphicx, tcolorbox, tabularx, tikz, booktabs, setspace}
\usepackage[compact]{titlesec}
\usepackage[margin=0.5in]{geometry}

\usepackage[backend=biber, style=apa, natbib=true, sorting=nyt, url=false,isbn=false, doi=false]{biblatex}

@@

\include{macros}
\newcommand{\imp}{\ensuremath{\rightarrow}}
\newcommand{\revimp}{\ensuremath{\leftarrow}}

\newcommand{\Type}{\ensuremath{\mathsf{Type}}}
\newcommand{\Set}{\ensuremath{\mathsf{Set}}}
\newcommand{\Prop}{\ensuremath{\mathsf{Prop}}}
\newcommand{\refl}[1]{\ensuremath{\mathsf{refl}\,{#1}}}
\newcommand{\mkmlidtype}[3]{{#1} =^{\mathrm{id}}_{#2} {#3}}
\newcommand{\mkmleqdep}[3]{{#1} =^{\mathrm{dep}}_{#2} {#3}}
\newcommand{\hrefl}[1]{\ensuremath{\mathsf{refl^{\mathrm{dep}}}\,{#1}}}
\newcommand{\mluniv}{\ensuremath{\mathsf{U}}}
\newcommand{\Jdep}[2]{\ensuremath{\mathsf{J}\;{#1}\;{#2}}}

@@

\newcommand{\sort}[1]{\ensuremath{\mathsf{U}_{#1}}}
\newcommand{\univ}{\boxempty}
\newcommand{\typeannot}{\mathsf{type}}
\newcommand{\istype}{~\typeannot}

@@

\newcommand{\defeq}{\ensuremath{\triangleq}}
\newcommand{\metaequiv}{\cong}
\newcommand{\metaletin}[3]{\mathit{let}\;{#1}\;\defeq\;{#2}\;\mathit{in}\;{#3}}
\newcommand{\map}[2]{\mathsf{ap}\,{#1}\,{#2}}
\newcommand{\depmap}[2]{\mathsf{apd}\,{#1}\,{#2}}
\newcommand{\transport}[3]{\mathsf{transport}\,{#1}\,{#2}\,{#3}}
\newcommand{\deptransport}[3]{\mathsf{transportd}\,{#1}\,{#2}\,{#3}}
\newcommand{\swap}[1]{{#1}^{\circ}}
\newcommand{\swapbracket}[1]{({#1})^{\circ}}
\newcommand{\swaptype}[1]{{#1}^{\circ}}
\newcommand{\swapoverdim}[2]{{#2}^{\mkoverdim{#1}{\circ}}}
\newcommand{\homsquare}[1]{\mathsf{homsquare}(#1)}
\newcommand{\permute}[2]{\mathsf{permute}_{#1}(#2)}
\newcommand{\swapprodeq}[2]{\mathsf{swap}_{\Pi=}^{#1}(#2)}
\newcommand{\swapeqprod}[2]{\mathsf{swap}_{=\Pi}^{#1}(#2)}
\newcommand{\swapeqprodlr}[2]{\mathsf{swap}_{=\Pi}^{\rightarrow}({#1})(#2)}
\newcommand{\swapeqprodrl}[2]{\mathsf{swap}_{=\Pi}^{\leftarrow}({#1})(#2)}
\newcommand{\swapsigmaeq}[1]{\mathsf{swap}_{\Sigma=}(#1)}
\newcommand{\swapeqsigma}[1]{\mathsf{swap}_{=\Sigma}(#1)}

@@

\newcommand{\heteroname}{het}
\newcommand{\mycubsetcomp}[2]{\ensuremath{\mathsf{cubset}_{#1}^{=#2}}}

@@

\newcommand{\mybox}[1]{\mathsf{box}_{#1}}
\newcommand{\mylayer}[1]{\mathsf{layer}_{#1}}
\newcommand{\mycube}[1]{\mathsf{\cubeovername}_{#1}}
\newcommand{\downbox}[2]{\mathsf{subbox}_{#1}^{#2}}
\newcommand{\downlayer}[2]{\mathsf{sublayer}_{#1}^{#2}}
\newcommand{\downcube}[2]{\mathsf{subcube}_{#1}^{#2}}
\newcommand{\cohbox}[2]{\mathsf{cohbox}_{{#1}}^{{#2}}}
\newcommand{\cohlayer}[2]{\mathsf{cohlayer}_{#1}^{#2}}
\newcommand{\cohcube}[2]{\mathsf{coh\cubeovername}_{#1,#2}}
\newcommand{\myfullbox}[2]{\ensuremath{\mathsf{fullbox}_{#1}^{#2}}}
\newcommand{\fulldownbox}[2]{\mathsf{subfullbox}_{#1}^{#2}}
\newcommand{\fulldowncube}[2]{\mathsf{subfullcube}_{#1}^{#2}}

@@

\newcommand{\expandheterocube}[2]{\mathsf{expand\Cubeovername}_{#1}^{#2}}
\newcommand{\expandheterolayer}[2]{\mathsf{expandLayer}_{#1}^{#2}}
\newcommand{\expanddownbox}[2]{\mathsf{expandsubbox}_{#1}^{#2}}
\newcommand{\expanddownlayer}[2]{\mathsf{expandsublayer}_{#1}^{#2}}
\newcommand{\expanddowncube}[2]{\mathsf{expandsubcube}_{#1}^{#2}}

\newcommand{\depdownbox}[2]{\mathsf{depsubbox}_{#1}^{#2}}
\newcommand{\depdownlayer}[2]{\mathsf{depsublayer}_{#1}^{#2}}
\newcommand{\depdowncube}[2]{\mathsf{depsubcube}_{#1}^{#2}}
\newcommand{\depdownboxbis}[2]{\mathsf{depsubliftbox}_{#1}^{#2}}
\newcommand{\depdownlayerbis}[2]{\mathsf{depsubliftlayer}_{#1}^{#2}}
\newcommand{\depdowncubebis}[2]{\mathsf{depsubliftcube}_{#1}^{#2}}
\newcommand{\depdownboxter}[2]{\mathsf{depsubliftbox'}_{#1}^{#2}}
\newcommand{\depdownlayerter}[2]{\mathsf{depsubliftlayer'}_{#1}^{#2}}
\newcommand{\depdowncubeter}[2]{\mathsf{depsubliftcube'}_{#1}^{#2}}

\newcommand{\depcohbox}[2]{\mathsf{depcohbox}_{#1}^{#2}}
\newcommand{\depcohlayer}[2]{\mathsf{depcohlayer}_{#1}^{#2}}
\newcommand{\depcohcube}[2]{\mathsf{depcohcube}_{#1}^{#2}}
\newcommand{\depcohboxbis}[2]{\mathsf{depcohliftbox}_{#1}^{#2}}
\newcommand{\depcohlayerbis}[2]{\mathsf{depcohliftlayer}_{#1}^{#2}}
\newcommand{\depcohcubebis}[2]{\mathsf{depcohliftcube}_{#1}^{#2}}
\newcommand{\depcohboxter}[2]{\mathsf{depcohliftbox'}_{#1}^{#2}}
\newcommand{\depcohlayerter}[2]{\mathsf{depcohliftlayer'}_{#1}^{#2}}
\newcommand{\depcohcubeter}[2]{\mathsf{depcohliftcube'}_{#1}^{#2}}

@@

\newcommand{\heterodownbox}[2]{\mathsf{sub{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterodownlayer}[2]{\mathsf{sub{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterodowncube}[2]{\mathsf{sub{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\depdownboxtype}[2]{\mathsf{Subdepbox}_{#1}^{#2}}
\newcommand{\depdownlayertype}[2]{\mathsf{Subdeplayer}_{#1}^{#2}}
\newcommand{\depdowncubetype}[2]{\mathsf{Subdep\cubeovername}_{#1}^{#2}}
\newcommand{\downboxtype}[2]{\mathsf{Subbox}_{#1}^{#2}}
\newcommand{\downlayertype}[2]{\mathsf{Sublayer}_{#1}^{#2}}
\newcommand{\downcubetype}[2]{\mathsf{Sub\cubeovername}_{#1}^{#2}}
\newcommand{\cohreflbox}[1]{\mathsf{cohreflbox}_{#1}}
\newcommand{\cohrefllayer}[1]{\mathsf{cohrefllayer}_{#1}}
\newcommand{\cohreflcube}[1]{\mathsf{cohreflcube}_{#1}}
\newcommand{\cohrefleqbox}[1]{\mathsf{cohrefleqbox}_{#1}}
\newcommand{\cohrefleqlayer}[1]{\mathsf{cohrefleqlayer}_{#1}}
\newcommand{\cohrefleqcube}[1]{\mathsf{cohrefleqcube}_{#1}}
\newcommand{\cohboxtype}[2]{\mathsf{Cohbox}_{#1}^{#2}}
\newcommand{\cohlayertype}[2]{\mathsf{Cohlayer}_{#1}^{#2}}
\newcommand{\cohcubetype}[2]{\mathsf{Coh\cubeovername}_{#1}^{#2}}
\newcommand{\heterocohbox}[2]{\mathsf{coh{\heteroname}box}_{#1}^{#2}}
\newcommand{\heterocohlayer}[2]{\mathsf{coh{\heteroname}layer}_{#1}^{#2}}
\newcommand{\heterocohcube}[2]{\mathsf{coh{\heteroname}\cubeovername}_{#1}^{#2}}
\newcommand{\myappdepbox}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdeplayer}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcube}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcube}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myappdepboxtype}[1]{\mathsf{homoappbox}_{#1}}
\newcommand{\myappdepfullboxtype}[1]{\mathsf{homoappfullbox}_{#1}}
\newcommand{\myappdeplayertype}[1]{\mathsf{homoapplayer}_{#1}}
\newcommand{\myappdepcubetype}[1]{\mathsf{homoapp\cubeovername}_{#1}}
\newcommand{\myappdepfullcubetype}[1]{\mathsf{homoappfullcube}_{#1}}
\newcommand{\myfullcube}[1]{\mathsf{fullcube}_{#1}}
\newcommand{\myfullheteroboxtype}[2]{\mathsf{fullBox}_{#1}^{#2}}
\newcommand{\myfullheterobox}[2]{\mathsf{full{\heteroname}box}_{#1}^{#2}}
\newcommand{\reflfullcube}[1]{\mathsf{reflfullcube}_{#1}}
\newcommand{\unitpoint}{\star}
\newcommand{\unittype}{\ensuremath{\mathsf{unit}}}
\newcommand{\eqett}{\equiv_{\mathit{ETT}}}
\newcommand{\reflett}{\mathsf{refl}_{\mathit{ETT}}}
\newcommand{\mygpd}{\mathsf{gpd}}

\newcommand{\mycubset}[1]{\mathsf{cubset}_{#1}}
\newcommand{\mycubsetfrom}[2]{\mathsf{cubset}_{#1}^{\geq#2}}
\newcommand{\partialcubset}[2]{\ensuremath{\mathsf{cubset}_{#1}^{<#2}}}
\newcommand{\mydepcubset}[1]{\mathsf{dephomocubset}_{#1}}
\newcommand{\mydepcubsetfrom}[2]{\mathsf{dephomocubset}_{#1}^{\geq#2}}
\newcommand{\mydepcubsetcomp}[2]{\mathsf{dephomocubset}_{#1}^{=#2}}
\newcommand{\deppartialcubset}[2]{\mathsf{dephomocubset}_{#1}^{<#2}}
\newcommand{\properheterocubetype}[2]{\mathsf{Filler}_{#1}^{#2}}

@@

\newcommand{\typecubset}{\mathsf{typecubset}}
\newcommand{\mysymcubset}{\mathsf{symcubset}}
\newcommand{\issymcubset}{\mathsf{issymcubset}}
\newcommand{\partialsymcubset}{\mathsf{symcubset}}
\newcommand{\mypermute}{\mathsf{permute}}
\newcommand{\partialhascomp}{\mathsf{partialhascomp}}
\newcommand{\hascomp}{\mathsf{hascomp}}
\newcommand{\tube}[1]{\mathsf{tube}_{#1}}
\newcommand{\propercube}[1]{\mathsf{properfiller}_{#1}}
\newcommand{\properheterocube}[2]{\mathsf{{\heteroname}filler}_{#1}^{#2}}
\newcommand{\border}[1]{\mathsf{border}_{#1}}
\newcommand{\bordertype}[1]{\mathsf{Boxofcube}_{#1}}
\newcommand{\cohbordertype}[1]{\mathsf{Cohboxofcube}_{#1}}
\newcommand{\myheteroborder}[1]{\mathsf{{\heteroname}border}_{#1}}
\newcommand{\fullheterocubetype}[2]{\mathsf{fullCube}_{#1}^{#2}}
\newcommand{\fullheterocube}[1]{\mathsf{full{\heteroname}cube}_{#1}}
\newcommand{\heterotubetype}[1]{\mathsf{Tube}_{#1}}
\newcommand{\heterotube}[1]{\mathsf{{\heteroname}tube}_{#1}}
\newcommand{\mygroundedcube}[1]{\mathsf{groundedcube}_{#1}}
\newcommand{\mygroundedheterocubetype}[1]{\mathsf{groundedCube}_{#1}}
\newcommand{\mygroundedheterocube}[1]{\mathsf{grounded{\heteroname}cube}_{#1}}
\newcommand{\reflexive}[1]{\mathsf{reflexive}_{#1}}
\newcommand{\permutation}{\mathsf{permutation}}
\newcommand{\diagonal}{\mathsf{diagonal}}
\newcommand{\connection}{\mathsf{connection}}
\newcommand{\diagprop}{\mathsf{diag}}
\newcommand{\reglr}{\rightarrow-\mathsf{reg}}
\newcommand{\regrl}{\leftarrow-\mathsf{reg}}
\newcommand{\coercivelr}{\rightarrow-\mathsf{def}}
\newcommand{\coerciverl}{\leftarrow-\mathsf{def}}
\newcommand{\regularitylr}{\rightarrow-\mathsf{regularity}}
\newcommand{\regularityrl}{\leftarrow-\mathsf{regularity}}
\newcommand{\Reglr}{\Rightarrow-\mathsf{reg}}
\newcommand{\Regrl}{\Leftarrow-\mathsf{reg}}
\newcommand{\Coercivelr}{\Rightarrow-\mathsf{def}}
\newcommand{\Coerciverl}{\Leftarrow-\mathsf{def}}
\newcommand{\Regularitylr}{\Rightarrow-\mathsf{regularity}}
\newcommand{\Regularityrl}{\Leftarrow-\mathsf{regularity}}
\newcommand{\coebacklr}{\overrightarrow{\mathsf{coe}}}
\newcommand{\coebackrl}{\overleftarrow{\mathsf{coe}}}
\newcommand{\backcoercivelr}{\overrightarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\backcoerciverl}{\overleftarrow{\mathsf{coe}}-\mathsf{def}}
\newcommand{\regbacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regbackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\regularitybacklr}{\overrightarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\regularitybackrl}{\overleftarrow{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Coebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}}
\newcommand{\Coercivebacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Coercivebackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{def}}
\newcommand{\Regbacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regbackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{reg}}
\newcommand{\Regularitybacklr}{\Overrightarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}
\newcommand{\Regularitybackrl}{\Overleftarrow{1ex}{\mathsf{coe}}-\mathsf{regularity}}

@@

% Simplicial set macros
\newcommand{\BDelta}{\ensuremath{\boldsymbol{\Delta}}}
\newcommand{\Simplex}[1][n]{\ensuremath{\boldsymbol{\Delta^{#1}}}}
\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
\newcommand{\SSet}{\ensuremath{\text{Set}_{\boldsymbol{\Delta}}}}

% The eqntable environment, displaying the various
\NewDocumentEnvironment{eqntable}{m}{\table[h!]\tabularx{\linewidth}{l c c c}}
{\endtabularx\caption{#1}\endtable}

% A block in the eqntable environment
\newcommand{\eqnline}[4]{#1 & #2 & #3 & #4 \\}
\newcommand{\mc}[1]{\multicolumn{4}{c}{\textit{#1}} \\\\}

@@

\section{Semi-cubical sets}

@@

          \myfullcube{l}^{n}     & (D,E)                                                                                          & \defeq & \Sigma d:\myfullbox{l}{n}(D).\, E.\mathsf{rel}(d) \\

@@

          \propercube{l}^{n}     & (D:\partialcubset{l}{n+1})~(d:\myfullbox{l}{n}(\hd(D)))                                        & :      & \sort{l}                                          \\

@@

          \border{l}^{n}         & (D:\partialcubset{l}{n+1})~(c:\mygroundedcube{l}^{n}(D))                                       & :      & \myfullbox{l}{n}(\hd(D))                          \\
